What We Eval in the Shadows

### 2021-04-17 paper/main.tex
Merge

Another instance, is the \emph{symbolic differentiation support} provided by base R package \emph{stats}, with two operators \c{D} and \c{deriv}. They support arithmetic operations and functions on real numbers such as \c{sin}, on expressions built with \c{expression()} or \c{parse}.
In \emph{MCMCglmm} (Monte Carl Markov Chain Generalised Linear Mixed Models), a \c{Dtensor} object is created: it contains expressions that are derived twice (with \c{DD}). To get a concrete value, it is evaluated in  dataframe \c{mu} where symbolic variables are bound to actual numbers.
\begin{lstlisting}
 expr<-expression(beta_1 + time*beta_2+u)
 mu = data.frame(beta_1=0.5, beta_2=1, time=3, u=2.3)
 D[i]<-eval(DD(expr, name[unlist(comb.pos[i,])]), mu)
\end{lstlisting}

@@

\Eval in R is mostly used for meta-programming purposes and to access
environments other than the local one. In Javascript, patterns are ad-hoc, such
as json loading and parsing, and can often be rewritten without \eval, such as
function or method call, or assignment to a local variable or an object
property. Compared to Javascript, \eval patterns in R we observed are much more
legitimate, although this is biased by the fact that our main corpus CRAN
features more experienced developers than  websites found at large on the web.
\todo{can we really claim that? SHould we talk about Kaggle there?}

\eval is a powerful tool and can be sometimes replaced with functions with more
specialized goals. For instance, variable lookup in any environment can be
performed with \c{get}, and assignment in any environment, with \c{assign}.
Building a call and executing can be done with \c{do.call}. Nevertheless, \eval
shines when expressions passed to it can be of many different types. % And it
is shorter to type, and no need to remember all the specialized functions, so
it is convenient.

Finally, let us mention an anecdotal use of \eval as a mean to bypass some
checks performed by the \c{R CMD CHECK} tool allowing one to submit a package
to CRAN that would otherwise be refused. For example, the tool checks that
packages do not call \c{unlockBinding} function.\footnote{It allows one to open
and modify loaded package name space.} Packages such as \c{data.table}
circumvent such restrictions by using \eval as the check is only performed
statically.

>>>>

Another instance is the \emph{symbolic differentiation support} provided by base R package \emph{stats}, with two operators \c{D} and \c{deriv}. They support arithmetic operations and functions on real numbers such as \c{sin}, on expressions built with \c{expression()} or \c{parse}.
In \emph{MCMCglmm} (Monte Carl Markov Chain Generalised Linear Mixed Models), a \c{Dtensor} object is created: it contains expressions that are derived twice (with \c{DD}). To get a concrete value, it is evaluated in  dataframe \c{mu} where symbolic variables are bound to actual numbers.
\begin{lstlisting}
 expr<-expression(beta_1 + time*beta_2+u)
 mu = data.frame(beta_1=0.5, beta_2=1, time=3, u=2.3)
 D[i]<-eval(DD(expr, name[unlist(comb.pos[i,])]), mu)
\end{lstlisting}

@@

\Eval in R is mostly used for meta-programming purposes and to access
environments other than the local one. In Javascript, patterns are ad-hoc, such
as json loading and parsing, and can often be rewritten without \eval, such as
function or method call, or assignment to a local variable or an object
property. Compared to Javascript, \eval patterns in R we observed are much more
legitimate, although this is biased by the fact that our main corpus CRAN
features more experienced developers than websites found at large on the web.

\eval is a powerful tool and can be sometimes replaced with functions with more
specialized goals. For instance, variable lookup in any environment can be
performed with \c{get}, and assignment in any environment, with \c{assign}.
Building a call and executing can be done with \c{do.call}. Nevertheless, \eval
shines when expressions passed to it can be of many different types.

Finally, let us mention an anecdotal use of \eval as a mean to bypass some
checks performed by the \c{R CMD CHECK} tool. This tool performs a numer of
well-formedness rules before accepting a package to the CRAN repository. Many
checks are performed statically, by looking at syntactic constructs in the R
code. Using \eval allows one to bypass such checks and thus submit a package to
CRAN that would otherwise be refused. For example, the it checks that packages
do not call \c{unlockBinding} function.\footnote{It allows one to open and
modify loaded package name space.} Packages such as \c{data.table} circumvent
such restrictions by using \eval as the check is only performed statically.
